\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-02-25 presentations/aarhus-25-02-2019/presentation.tex
Add Aarhus February presentation

\begin{document}
\maketitle

@@

@@

\begin{frame}
  \frametitle{Attack on naive stack and return capabilities }
  \centering
  \begin{tikzpicture}[scale=.45, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

\begin{frame}
  \frametitle{\stktokens{} prevent the attack}
  % Emphazise that it is dynamically enforced.
  % Other cases, see paper.
  \centering
  \begin{tikzpicture}[scale=.45, every node={scale=.5}]
    % recurrent parts
    \stdstackstart
    \draw (17.5,5.5) node {register file};
    \begin{scope}
      \clip (16.9,1.1) rectangle (18.1,5.1);
      \foreach \x in {1,2,...,4}
      {
        \draw[fill=white] (17,\x) rectangle (18,\x+1) node[pos=.5,color=mygreen] {};
      };
    \end{scope}
    \node (r1) at (17.75,4.5) {};
    \node (r2) at (17.75,3.6) {};

@@

@@

\section{Defining well-bracketed control flow and local state encapsulation by fully-abstract overlay semantics}
\begin{frame}[fragile]
  \frametitle{Well-bracketed control flow and local state encapsulation}
  \begin{columns}
    \begin{column}{0.5\textwidth}
\begin{lstlisting}[language=C, escapechar=!]
!\tikz[remember picture] \node[] (a) {};!void a()       !\tikz[remember picture] \node[] (bt) {};! 
 {
   !\tikz[remember picture] \node[] (pc6) {};!...
   !\tikz[remember picture] \node[] (pc7) {};!return;!\tikz[remember picture] \node[] (ret) {};!      
 }              !\tikz[remember picture] \node[] (bb) {};!

@@

% \begin{frame}
%   \frametitle{Fully-abstract overlay semantics}
%   \begin{columns}
% \begin{column}{0.5\textwidth}
%   \begin{itemize}[<+->]
%   \item Compile from oLCM to LCM
%   \item Compilation is the identity
%   \item Builtin call stack abstraction in oLCM preserved after compilation
%   \end{itemize}
% \end{column}
% \begin{column}{0.5\textwidth}
%   \begin{tikzpicture}
%     \draw (0,0) node[draw=black, rounded corners] (olcm) {oLCM};
%     \draw node[draw=black, rounded corners,below=2.5cm of olcm] (lcm) {LCM};
%     \draw (olcm) edge[bend left, ->,thick] (lcm);
%     \draw node[left = 3cm of olcm] (ll1) {};
%     \draw node[right = 3cm of olcm] (rl1) {};
%     \draw node[below = 1.25cm of ll1] (ll) {};
%     \draw node[below = 1.25cm of rl1] (rl) {};
%     \draw[dashed] (ll) -- (rl);

>>>>

\begin{document}
\beamertemplatenavigationsymbolsempty
\maketitle

@@

\begin{frame}[fragile]
  \frametitle{Well-bracketed control flow and local state encapsulation}
  \begin{columns}
    \begin{column}{0.5\textwidth}
\begin{lstlisting}[language=C, escapechar=!]
!\tikz[remember picture] \node[] (a) {};!void a()       !\tikz[remember picture] \node[] (bt) {};! 
 {
   !\tikz[remember picture] \node[] (pc6) {};!...
   !\tikz[remember picture] \node[] (pc7) {};!return;!\tikz[remember picture] \node[] (ret) {};!      
 }              !\tikz[remember picture] \node[] (bb) {};!

@@

\begin{frame}
  \frametitle{Attack 1 on naive stack and return capabilities }
  \centering
  \begin{tikzpicture}[scale=.45, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

\begin{frame}
  \frametitle{\stktokens{}}
  \begin{itemize}
  \item Check the base address of the stack capability before and after calls.
  \item Make sure that local stack frames are non-empty.
    % Not illustrated. Trusted code must claim spot on the call stack to make
    % sure that they are returned to.
  \item Create token and data return capability on call: split the stack
    capability in two to get a stack capability for your local stack frame and a
    stack capability for the unused part of the stack. The former is sealed and
    used for the data part of the return pair.
  \item Create code return capability on call: Seal the old program pointer.
  \item Reasonable use of seals: Return seals are only used to seal old program
    pointers, every return seal is only used for one call site, and they are not
    leaked. % If return seals are used for other things, like sealing arbitrary
            % code pointers, then they can be used as an unsealing mechanism.
            % If the same seal is used for multiple call sites, then we lose the
            % guarantee that we return to the correct place. One could use the
            % wrong return capability to return "out of order"
            % If return seals are leaked, then we have no guarantee about what
            % they are used for.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{\stktokens{} prevent attack 1}
  % Emphazise that it is dynamically enforced.
  % Other cases, see paper.
  \centering
  \begin{tikzpicture}[scale=.45, every node={scale=.5}]
    % recurrent parts
    \stdstackstart
    \draw (17.5,5.5) node {register file};
    \begin{scope}
      \clip (16.9,1.1) rectangle (18.1,5.1);
      \foreach \x in {1,2,...,4}
      {
        \draw[fill=white] (17,\x) rectangle (18,\x+1) node[pos=.5,color=mygreen] {};
      };
    \end{scope}
    \node (r1) at (17.75,4.5) {};
    \node (r2) at (17.75,3.6) {};

@@

\begin{frame}
  \frametitle{Attack 2 on naive stack and return capabilities }
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

    % first step: capabilities
    \begin{onlyenv}<+>
      \draw[fill=white] (0,2.5) rectangle (6,4) node[pos=.5] {\footnotesize current stack frame};
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
        (6.5,2.5) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
      % \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      % (6,0) -- (6,16) node (oldframe1) [black,midway,xshift=0.5cm] {};
      % \draw node[fill=gray!50,right=0cm of oldframe1] (rp1l) {return pointer data};
    \end{onlyenv}

    % attacker stores copy of stack pointer high in the stack
    \draw<+->[fill=gray!50] (0,2.5) rectangle (6,4) node[pos=.5] {\footnotesize caller stack frame};
    \begin{onlyenv}<.-.(2)>
      \actadv{(0,4)}{(6,7)}{callee stack frame}
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
        (6.5,4) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
    \end{onlyenv}
    \draw<+->[fill=white] (0,13) rectangle (6,13.5) node[pos=.5,color=myred] {\footnotesize copy of sp};
    \draw<.> (6,13.25) edge[myred,thick,->,in=45] (sp1);
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
        (13.5,4) -- (13.5,16) node[draw=black] (spold) [black,midway,xshift=0.8cm] {};
      \draw (6,13.25) edge[myred,thick,->,in=45] (spold);
    \end{onlyenv}

    % attacker calls trusted code again
%    \draw<+->[fill=gray!50] (0,4) rectangle (6,7) node[pos=.5] {\footnotesize callee stack frame};
    \begin{onlyenv}<+->
      \inactadv{(0,4)}{(6,7)}{callee stack frame}
    \end{onlyenv}
    \begin{onlyenv}<.>
      \draw[fill=white] (0,7) rectangle (6,9) node[pos=.5] {\footnotesize callee (2) stack frame};
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
        (6.5,7) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
    \end{onlyenv}

    % attacker uses old stack pointer
    \draw<+->[fill=gray!50] (0,7) rectangle (6,9) node[pos=.5] {\footnotesize callee (2) stack frame};
    \begin{onlyenv}<.-.(1)>
      \actadv{(0,9)}{(6,12)}{callee (3) stack frame}
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,9) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
    \end{onlyenv}
    \draw<+> (spold) edge[->,color=myred,very thick,out=235,in=0] node[sloped, below] {read/write} (6,8);
  \end{tikzpicture}
\end{frame}

\begin{frame}
  \frametitle{\stktokens{} prevent attack 2}
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

    \draw (16.5,5.5) node {register file};
    \begin{scope}
      \clip (15.9,1.1) rectangle (17.1,5.1);
      \foreach \x in {1,2,...,4}
      {
        \draw[fill=white] (16,\x) rectangle (17,\x+1) node[pos=.5,color=mygreen] {};
      };
    \end{scope}
    \node (r1) at (16.75,4.5) {};
    \node (r2) at (16.75,3.6) {};

    % Caller 
    \actsf{(0,2.5)}{(6,5)}{caller stack frame} 
    \begin{onlyenv}<+>
      \capbrace{(6.5,2.5)}{(6.5,16)}
      \draw node[right=0cm of sp1] { stack pointer };
      \draw (r1) edge[->,myred,thick,bend left,dashed] (sp1);
    \end{onlyenv}

    % Split the stack pointer
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \capbrace[usp]{(6.5,5)}{(6.5,16)}
      \draw (r2) edge[->,myred,thick,bend left,dashed] (sp2);
      \draw (r1) edge[->,myred,thick,bend left, dashed] (usp);
      \draw node[right=0cm of usp] { stack pointer };
      \draw node[right=0cm of sp2] { private stack pointer };
    \end{onlyenv}

    % Callee called
    \begin{onlyenv}<+>
      \capbrace[usp]{(6.5,5)}{(6.5,16)}
      \draw (r1) edge[->,myred,bend left,dashed] (usp);
      \draw node[right=0cm of usp] { stack pointer };
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actadv{(0,5)}{(6,8)}{callee stack frame}
    \end{onlyenv}

    \begin{onlyenv}<.->
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw node[fill=gray!50,right=0cm of sp2] { \phantom{return data pointer} };
      \draw (r2) edge[->,myred,bend left,dashed] (sp2);
      \draw node[right=0cm of sp2] { return data pointer };
    \end{onlyenv}

    \begin{onlyenv}<+>

      \capbrace[usp]{(13.5,5)}{(13.5,16)}
      \draw (6,13.25) edge[myred,thick,->,in=45,dashed] (usp);
      \draw node[right=0cm of usp] { stack pointer };

      \draw[fill=white] (0,13) rectangle (6,13.5) node[pos=.5,color=myred] {\footnotesize sp};
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actadv{(0,5)}{(6,8)}{callee stack frame}
    \end{onlyenv}

    % At this point we have a linear point stored in a part of memory that it governs. In other words, no other capabilities can grant access to this part of memory, to the capabilitiy is essentially lost.
%    \draw<+> node[mygreen,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (4,10) { Stack pointer\\essentially lost.};

    \begin{onlyenv}<+->

      \capbrace[usp]{(13.5,5)}{(13.5,16)}
      \draw (6,13.25) edge[myred,thick,->,in=45,dashed] (usp);
      \draw node[right=0cm of usp] { stack pointer };

      \begin{scope}
        \fill[fill=gray!50] (0,2.5) rectangle (6,15) node[pos=.5,color=black] {};
        \draw (0,0) -- (0,15);
        \draw (6,0) -- (6,15);
      \end{scope}
      \draw[fill=gray!50] (0,13) rectangle (6,13.5) node[pos=.5,color=myred,dashed] {\footnotesize sp};
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \inactadv{(0,5)}{(6,8)}{callee stack frame}
      \actsf{(0,8)}{(6,10.5)}{callee (2) stack frame} 
  \end{onlyenv}

  \draw<+>[mygreen,very thick] (-0.5,7.5) -- (6.5,11);
  \draw<.>[mygreen,very thick] (-0.5,11) -- (6.5,7.5);
  \draw<.> node[mygreen,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (14,7) { No stack pointer\\for callee (2)!};

  \end{tikzpicture}
\end{frame}

\begin{frame}
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    \frametitle{Attack 3 on naive stack and return capabilities}
    \begin{scope}
    \clip (-.1,-.1) rectangle (5.1,10.1);
    \fill[fill=gray!50] (0,0) rectangle (5,10);
    \draw (0,0) -- (0,10);
    \draw (5,0) -- (5,10);
    \end{scope}
    \draw (2.5,11) node {code memory};

    \begin{scope}
    \clip (12.9,3.9) rectangle (18.1,11.1);
    \fill[fill=gray!50] (13,4) rectangle (18,11);
    \draw (13,4) -- (13,11);
    \draw (18,4) -- (18,11);
    \end{scope}
    \draw (15.5,12) node {more code memory};

    \begin{scope}
    \clip (12.9,-.1) rectangle (18.1,2.1);
    \fill[fill=gray!50] (13,0) rectangle (18,2);
    \draw (13,0) -- (13,2);
    \draw (18,0) -- (18,2);
    \end{scope}
    \draw (14.5,3) node {heap memory};

\note{Caller calls callee}
    \draw<+->[fill=white] (0,1) rectangle (5,4) node[pos=.5] {\footnotesize caller code};

    \begin{onlyenv}<+->
      \capbrace[ret1]{(5.1,1)}{(5.1,4)}
      \draw node[fill=gray!50, right=0cm of ret1] { \phantom{ret-ptr} };
      \draw node[right=0cm of ret1] { ret-ptr };
    \end{onlyenv}

\note{Callee has access to some place to store things.}
    \begin{onlyenv}<+->
      \draw[fill=gray!30] (0,1) rectangle (5,4) node[pos=.5] {\footnotesize caller code};
      \draw[fill=white] (13,5) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
      \draw[fill=white] (13,1) rectangle (18,1.5) node[pos=.5] {};
    \end{onlyenv}

    \begin{onlyenv}<.-.(2)>
      \draw [decorate,decoration={brace,amplitude=2pt,mirror,raise=4pt},yshift=0pt]
      (18.1,1) -- (18.1,1.5) node[draw=black] (copy) [black,midway,xshift=0.5cm] {};
      \draw (18,5.5)  edge[->,bend left] (copy);
    \end{onlyenv}

\note{Callee stores the return pointer they got from caller.}
    \begin{onlyenv}<+->
      \draw[fill=white] (13,1) rectangle (18,1.5) node[pos=.5] {\scriptsize {\color{myred} copy of ret-ptr}};
      \draw (13,1.25) edge[->,myred,thick,bend left] (ret1);
    \end{onlyenv}

\note{Callee calls callee (1)}
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=3pt,raise=4pt},yshift=0pt]
      (12.9,5) -- (12.9,6) node[draw=black] (ret2) [black,midway,xshift=-0.8cm] {};
      \draw node[fill=gray!50,left=0cm of ret2] { \phantom{ret-ptr (1)} };
      \draw node[left=0cm of ret2] (retptr1) { ret-ptr (1) };
    \end{onlyenv}

    \begin{onlyenv}<+->
      \draw[fill=white] (0,5) rectangle (5,8) node[pos=.5] {\footnotesize callee code (1)};
      \draw[fill=gray!30] (13,5) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
      \draw[fill=gray!30] (13,1) rectangle (18,1.5) node[pos=.5] {\scriptsize {\color{myred} copy of ret-ptr}};
    \end{onlyenv}

\note{Callee (1) calls callee (2)}
    \begin{onlyenv}<+->
      \capbrace[ret3]{(5.1,5)}{(5.1,8)}
      \draw node[fill=gray!50,right=0cm of ret3] { \phantom{ret-ptr (2)} };
      \draw node[right=0cm of ret3] (retptr2) { ret-ptr (2) };
    \end{onlyenv}

    \begin{onlyenv}<+->
      \draw[fill=gray!30] (0,5) rectangle (5,8) node[pos=.5] {\footnotesize callee code (1)};
      \draw[fill=white] (13,7) rectangle (18,10) node[pos=.5] {\footnotesize callee code (2)};
    \end{onlyenv}
\note{Callee (2) colludes with callee}
    \begin{onlyenv}<+->
      \draw (21,7.5) node[devil,opaque=0.5,mirrored,minimum size=1cm] {};
    \end{onlyenv}
\note{Callee (2) has access to ret-ptr (the return pointer caller passed to callee)}
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=2pt,mirror,raise=4pt},yshift=0pt]
      (18.1,1) -- (18.1,1.5) node[draw=black] (copy) [black,midway,xshift=0.5cm] {};
      \draw (18,8.25)  edge[->,myred,thick,bend left] (copy);
      \draw[fill=white] (13,1) rectangle (18,1.5) node[pos=.5] {\scriptsize {\color{myred} copy of ret-ptr}};
    \end{onlyenv}

\note{Callee (2) uses ret-ptr to return}
    \begin{onlyenv}<+->
      \draw[fill=gray!30] (13,7) rectangle (18,10) node[pos=.5] {\footnotesize callee code (2)};
      \draw[fill=white] (0,1) rectangle (5,4) node[pos=.5] {\footnotesize caller code};
      \draw[fill=gray!30] (13,1) rectangle (18,1.5) node[pos=.5] {\scriptsize {\color{myred} copy of ret-ptr}};
    \end{onlyenv}

    \note{This breaks well-bracketedness as ret-ptr (2) and ret-ptr (1) was not returned to}
    \begin{onlyenv}<+->
      \draw node [ellipse, fit=(retptr1) (retptr2), draw, myred] { };
      \draw node[myred,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (12,10) { These were skipped!};  
    \end{onlyenv}
  \end{tikzpicture}
\end{frame}

\begin{frame}
  \frametitle{\stktokens{} prevent attack 3}
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
  \scope
    \clip (-.1,-.1) rectangle (6.1,15.1);
    \fill[fill=white] (0,0) rectangle (6,15);
    \draw (0,0) -- (0,15);
    \draw (6,0) -- (6,15);
    \draw[fill=gray!50] (0,-.5) rectangle (6,1.5) node[pos=.5,color=black] {\footnotesize higher stack frames...};
  \endscope
  % \draw[->] (-2,0) -- node[midway,sloped,above] {stack grows upward} (-2,15);

  \begin{scope}
    \fill[gray!50] (13,0) rectangle (18,13);
    \draw (13,0) -- (13,13);
    \draw (18,0) -- (18,13);
    \draw (15.5,14) node {code memory};
  \end{scope}

\note{Caller calls callee (split stack pointer to make ret-ptr-d)}
  \begin{onlyenv}<+->
    \actsf{(0,1.5)}{(6,4.5)}{caller stack frame}
    \draw[fill=white] (13,1) rectangle (18,3) node[pos=.5] {\footnotesize caller code};
  \end{onlyenv}
  \begin{onlyenv}<.>
    \capbrace[sp]{(6.1,1.5)}{(6.1,15)}
    \draw node[right=0cm of sp] { sp };
  \end{onlyenv}

  \begin{onlyenv}<+->
    \capbrace[ret1]{(6.1,1.5)}{(6.1,4.5)}
    \draw node[fill=gray!50,right=0cm of ret1] { \phantom{ret-ptr-d} };
    \draw node[right=0cm of ret1] { ret-ptr-d };
  \end{onlyenv}
  \begin{onlyenv}<.->
    \draw [decorate,decoration={brace,aspect=0.3,amplitude=4pt,raise=4pt},yshift=0pt]
    (12.9,1) -- (12.9,3) node[draw=black] (ret1c) [black,pos=0.3,xshift=-0.6cm] {};
    \draw node[fill=gray!50,left=0cm of ret1c] { \phantom{ret-ptr-c} };
    \draw node[left=0cm of ret1c] { ret-ptr-c };
  \end{onlyenv}

  \begin{onlyenv}<.-.(3)>
    \capbrace[sp]{(6.1,4.5)}{(6.1,15)}
    \draw node[right=0cm of sp] { sp };
  \end{onlyenv}

  \begin{onlyenv}<+-+(3)>
    \draw[fill=gray!30] (13,1) rectangle (18,3) node[pos=.5] {\footnotesize caller code};
    \draw[fill=white] (13,4) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
    \actadv{(0,4.5)}{(6,7.5)}{callee stack frame}
    \inactsf{(0,1.5)}{(6,4.5)}{caller stack frame}
  \end{onlyenv}

\note{Callee saves ret-ptr-d on the heap.}
  \begin{onlyenv}<+->
    \draw (13,4.75) edge[myred,bend right,thick,->,dashed] (ret1);
  \end{onlyenv}
\note{Callee saves ret-ptr-c on the heap.}
  \begin{onlyenv}<+->
    \draw (13,4.75) edge[myred,bend right,thick,->] (ret1c);
  \end{onlyenv}

\note{Callee calls callee (1)}
\note{Before the callee jumps, it is assumed that it has checked the global "max height" of its stack pointer!}
  \begin{onlyenv}<+-+(4)>
    \capbrace[ret2]{(6.1,4.5)}{(6.1,7.5)}
    \draw node[fill=gray!50,right=0cm of ret2] { \phantom{ret-ptr-d (1)} };
    \draw node[right=0cm of ret2] { ret-ptr-d (1) };
  \end{onlyenv}
  \begin{onlyenv}<.-.(1)>
    \capbrace[sp]{(6.1,7.5)}{(6.1,15)}
    \draw node[right=0cm of sp] { sp };
  \end{onlyenv}

  \begin{onlyenv}<+-+(1)>
    \inactsf{(0,1.5)}{(6,4.5)}{caller stack frame}
    \inactadv{(0,4.5)}{(6,7.5)}{callee stack frame}
    \actsf{(0,7.5)}{(6,10.5)}{callee stack frame (1)}
    \draw[fill=gray!30] (13,1) rectangle (18,3) node[pos=.5] {\footnotesize caller code};
    \draw[fill=gray!30] (13,4) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
    \draw[fill=white] (13,7) rectangle (18,9) node[pos=.5] {\footnotesize callee code (1)};
  \end{onlyenv}

\note{Callee (1) calls callee (2)}
  \begin{onlyenv}<+-+(2)>
    \capbrace[ret3]{(6.1,7.5)}{(6.1,10.5)}
    \draw node[fill=gray!50,right=0cm of ret3] { \phantom{ret-ptr-d (2)} };
    \draw node[right=0cm of ret3] { ret-ptr-d (2) };
  \end{onlyenv}
  \begin{onlyenv}<.->
    \capbrace[sp]{(6.1,10.5)}{(6.1,15)}
    \draw node[right=0cm of sp] { sp };
  \end{onlyenv}

  \begin{onlyenv}<+->
    \inactsf{(0,1.5)}{(6,4.5)}{caller stack frame}
    \inactadv{(0,4.5)}{(6,7.5)}{callee stack frame}
    \inactsf{(0,7.5)}{(6,10.5)}{callee stack frame (1)}
  \end{onlyenv}

  \begin{onlyenv}<.->
    \draw[fill=gray!30] (13,1) rectangle (18,3) node[pos=.5] {\footnotesize caller code};
    \draw[fill=gray!30] (13,4) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
    \draw[fill=gray!30] (13,7) rectangle (18,9) node[pos=.5] {\footnotesize callee code (1)};
    \draw[fill=white] (13,10) rectangle (18,12) node[pos=.5] {\footnotesize callee code (2)};
  \end{onlyenv}
  \begin{onlyenv}<.-.(1)>
    \actadv{(0,10.5)}{(6,13.5)}{callee stack frame (2)}
  \end{onlyenv}

\note{Callee (2) has a capability for Callee and can thus access the stored ret-ptr-d}
  \begin{onlyenv}<+->
    \draw [decorate,decoration={brace,amplitude=4pt,mirror,raise=4pt},yshift=0pt]
    (18.1,4) -- (18.1,6) node[draw=black] (calleecap) [black,midway,xshift=0.6cm] {};
    \draw (18,11) edge[myred,bend left,thick,->] (calleecap);
  \end{onlyenv}

\note{Callee (2) uses ret-ptr-d to return}
  \begin{onlyenv}<+->
    \actsf{(0,1.5)}{(6,4.5)}{caller stack frame}
    \draw node[fill=white,right=0cm of ret1] { ret-ptr-d };
    \draw node[fill=white,left=0cm of ret1c] { ret-ptr-c };
    \draw (13,4.75) edge[myred,bend right,thick,->,dashed] (ret1);
  \end{onlyenv}

  \begin{onlyenv}<+->
    \draw[mygreen,very thick] (6.4,4.4) -- (7.4,5.4);
    \draw[mygreen,very thick] (7.4,4.4) -- (6.4,5.4);
    \draw node[mygreen,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (10,6) { Splice fails!};  
  \end{onlyenv}

\note{Splicing: fails because ends of capabilities don't meet. callee stack frame (1) cannot be empty (it will at least contain 42).}
  % \begin{onlyenv}<+->
  %   \draw node[mygreen,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (8,7.5) {Caller tries to splice sp \\and ret-ptr-d, but fails!};  
  % \end{onlyenv}
\note{Before the caller makes another call/return, it will check that the stack height matches the global max stack height.}
\end{tikzpicture}
\end{frame}

\begin{frame}
  \frametitle{\stktokens{} enforces single stack}
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
  \scope
    \clip (-.1,-.1) rectangle (6.1,15.1);
    \fill[fill=white] (0,0) rectangle (6,15);
    \draw (0,0) -- (0,15);
    \draw (6,0) -- (6,15);
    \draw[fill=gray!50] (0,-.5) rectangle (6,1.5) node[pos=.5,color=black] {\footnotesize higher stack frames...};
  \endscope
  % \draw[->] (-2,0) -- node[midway,sloped,above] {stack grows upward} (-2,15);

  \begin{scope}
    \fill[gray!50] (13,0) rectangle (18,13);
    \draw (13,0) -- (13,13);
    \draw (18,0) -- (18,13);
    \draw (15.5,14) node {heap};
  \end{scope}

\note{Caller calls callee (split stack pointer to make ret-ptr-d)}
  \begin{onlyenv}<+>
    \actsf{(0,1.5)}{(6,4.5)}{caller stack frame}
  \end{onlyenv}
  \begin{onlyenv}<.>
    \capbrace[sp]{(6.1,1.5)}{(6.1,15)}
    \draw node[right=0cm of sp] { sp };
  \end{onlyenv}

  \begin{onlyenv}<+->
    \inactsf{(0,1.5)}{(6,4.5)}{caller stack frame}
  \end{onlyenv}
  \begin{onlyenv}<.>
    \actadv{(0,4.5)}{(6,7.5)}{callee stack frame}
    \draw[fill=white] (13,6) rectangle (18,9) node[pos=.5] {\footnotesize adv mem};
  \end{onlyenv}
  \begin{onlyenv}<.>
    \capbrace[sp2]{(6.1,4.5)}{(6.1,15)}
    \capbrace[sp]{(6.1,1.5)}{(6.1,4.5)}
    \draw node[right=0cm of sp2] { sp2 };
    \draw node[right=0cm of sp, fill=gray!50] { ret-ptr-d };
    \draw (13,6.5) edge[myred,bend right,thick,->,dashed] (sp);
  \end{onlyenv}

  \begin{onlyenv}<+>
    \capbrace[sp3]{(6.1,9.5)}{(6.1,15)}
    \capbrace[sp2]{(6.1,4.5)}{(6.1,9.5)}
    \capbrace[sp]{(6.1,1.5)}{(6.1,4.5)}
    \draw node[right=0cm of sp3] { sp3 };
    \draw node[right=0cm of sp2] { sp2 };
    \draw node[right=0cm of sp, fill=gray!50] { ret-ptr-d };
    \draw (13,7.5) edge[myred,bend right,thick,->,dashed] (sp2);
    \draw (13,6.5) edge[myred,bend right,thick,->,dashed] (sp);
  \end{onlyenv}
  \begin{onlyenv}<.->
    \actsf{(0,9.5)}{(6,11.5)}{callee stack frame (1)}
  \end{onlyenv}
  \begin{onlyenv}<.>
    \inactadv{(0,4.5)}{(6,7.5)}{callee stack frame}
    \draw[fill=gray!30] (13,6) rectangle (18,9) node[pos=.5] {\footnotesize adv mem};
  \end{onlyenv}

  \begin{onlyenv}<+>
    \capbrace[sp4]{(6.1,11.5)}{(6.1,15)}
    \capbrace[sp3]{(6.1,9.5)}{(6.1,11.5)}
    \capbrace[sp2]{(6.1,4.5)}{(6.1,9.5)}
    \capbrace[sp]{(6.1,1.5)}{(6.1,4.5)}
    \draw node[right=0cm of sp4] { sp4 };
    \draw node[right=0cm of sp3, fill=gray!50] { sp3 };
    \draw node[right=0cm of sp2] { sp2 };
    \draw node[right=0cm of sp, fill=gray!50] { ret-ptr-d };
    \draw (13,8.5) edge[myred,bend right,thick,->,dashed] (sp3);
    \draw (13,7.5) edge[myred,bend right,thick,->,dashed] (sp2);
    \draw (13,6.5) edge[myred,bend right,thick,->,dashed] (sp);
  \end{onlyenv}
  \begin{onlyenv}<.->
    \inactsf{(0,9.5)}{(6,11.5)}{callee stack frame (1)}
    \actadv{(0,11.5)}{(6,14.5)}{callee stack frame (2)}
  \end{onlyenv}
  \begin{onlyenv}<.>
    \actadv{(0,4.5)}{(6,7.5)}{callee stack frame}
    \draw[fill=white] (13,6) rectangle (18,9) node[pos=.5] {\footnotesize adv mem};
  \end{onlyenv}

  \begin{onlyenv}<+->
    \capbrace[sp4]{(6.1,11.5)}{(6.1,15)}
    \capbrace[sp3]{(6.1,9.5)}{(6.1,11.5)}
    \capbrace[sp]{(6.1,1.5)}{(6.1,9.5)}
    \draw node[right=0cm of sp4, fill=gray!50] { sp4 };
    \draw node[right=0cm of sp3, fill=gray!50] { sp3 };
    \draw node[right=0cm of sp] { sp };
    \draw (13,8.5) edge[myred,bend right,thick,->,dashed] (sp3);
  \end{onlyenv}
  \begin{onlyenv}<.->
    \inactsf{(0,9.5)}{(6,11.5)}{callee stack frame (1)}
    \inactadv{(0,11.5)}{(6,14.5)}{callee stack frame (2)}
    \actsf{(0,1.5)}{(6,4.5)}{caller stack frame}
    \draw[fill=white] (13,6) rectangle (18,9) node[pos=.5] {\footnotesize adv mem};
  \end{onlyenv}
  \begin{onlyenv}<+->
    \draw[mygreen,very thick] (2.5,10) -- (3.5,9);
    \draw[mygreen,very thick] (3.5,10) -- (2.5,9);
    \draw node[mygreen,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center, anchor=west] () at (4,9.5) { Base check fails!};  
  \end{onlyenv}
\end{tikzpicture}
\end{frame}

@@

% \begin{frame}
%   \frametitle{\stktokens{}: ``Base address'' check}
%   \includegraphics[width=\textwidth]{stk-fig1}
% \end{frame}

\begin{frame}
  \frametitle{\stktokens{} summary}
  \setbeamercovered{transparent}
  \begin{itemize}
  \item<0> Check the base address of the stack capability before and after calls.
  \item<1> Make sure that local stack frames are non-empty.
    % Not illustrated. Trusted code must claim spot on the call stack to make
    % sure that they are returned to.
  \item<0> Create token and data return capability on call: split the stack
    capability in two to get a stack capability for your local stack frame and a
    stack capability for the unused part of the stack. The former is sealed and
    used for the data part of the return pair.
  \item<0> Create code return capability on call: Seal the old program pointer.
  \item<2> Reasonable use of seals: Return seals are only used to seal old program
    pointers, every return seal is only used for one call site, and they are not
    leaked. % If return seals are used for other things, like sealing arbitrary
            % code pointers, then they can be used as an unsealing mechanism.
            % If the same seal is used for multiple call sites, then we lose the
            % guarantee that we return to the correct place. One could use the
            % wrong return capability to return "out of order"
            % If return seals are leaked, then we have no guarantee about what
            % they are used for.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{\stktokens{} FAQ}
  \begin{itemize}
  \item \textit{Do you support tail calls?}
    \begin{itemize}
    \item Yes.
    \end{itemize}
  \item \textit{Do you support higher-order functions?}
    \begin{itemize}
    \item Yes.
    \end{itemize}
  \end{itemize}
\end{frame}

\section{Defining well-bracketed control flow and local state encapsulation by fully-abstract overlay semantics}

@@

\begin{frame}
  \frametitle{Proof sketch for a realistic secure compiler}
  \begin{center}
  \begin{tikzpicture}[scale=.5, every node={scale=.5},distance=1cm]
    % \draw<1-6> (-5,0) node {};
    % \draw (5,0) node {};
    % \draw (0,-14) node {};
    \draw<1-> node[draw=black,rounded corners,above] (source) {High-level language};
    \draw<1-> node[draw=black,rounded corners,below=of source] (mca) {Machine code w/ many abstractions};
    \draw<1-> node[draw=black,rounded corners,below=1cm of mca] (mcir) {...};
    \draw<1-> node[draw=black,rounded corners,below=1cm of mcir] (mcs) {Machine code w/ built-in stack};
    \draw<1-> node[draw=black,rounded corners,below=of mcs] (target) {Machine code};
